DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-11-14 scnn.tex
typo

Our graph is constructed as an approximation of sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$,
Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
While our construction will not exactly respect the setting defined by \citep{belkin2007convergence}, we observe empirically strong evidence of convergence.

>>>>

Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
While our construction will not exactly respect the setting defined by \citep{belkin2007convergence}, we observe empirically strong evidence of convergence.
